Software Ticket Quality

### 2017-12-05 proposal/mprop.tex
Finish background survey draft

However, the work of \citet{turney2002thumbs} looks only at sentiment analysis without
examining the context.

\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The paper's main goal is to find efficient ways to distinguish between 
    contextual and prior polarity.
  \item \textbf{What was the method?}
    They used a two step method that used machine learning and a variety of
    features. The first step classified each phrase which had a clue as either
    neutral or polar, followed by taking all phrases marked in the previous step
    and giving them a contextual polarity (e.g.\ positive, negative, 
    both, neutral).
  \item \textbf{What did they learn?}
    Through the method the authors employed, they managed to automatically 
    identify the contextual polarity. As most papers were only looking at the 
    sentiment extracted from the overall document, they managed to get valuable 
    results from looking at specific words and phrases.
  \item \textbf{Relevance to our work}: when analyzing the description and
    comments of the ticket, we can use their method for infering the sentiment 
    transmitted probably more accurately than the technique used in 
    Turney's paper\cite{turney2002thumbs}.
\end{itemize}

\subsection{Conclusion}

>>>>

However, the work of \citet{turney2002thumbs} looks only at sentiment analysis without
examining the context. The research from \citet{wilson2005recognizing} tries to find
efficient ways to distinguish between contextual and prior polarity. They used a two 
step method that used machine learning and a variety of features. The first step 
classified each phrase which had a clue as either neutral or polar, followed by 
taking all phrases marked in the previous step and giving them a contextual polarity 
(e.g. positive, negative, both, neutral). Through the method the authors employed,
they managed to automatically identify the contextual polarity. As most papers were only
looking at the sentiment extracted from the overall document, they managed to get 
valuable results from looking at specific words and phrases.
